---
title: "`r report_title`"
author: "Generated by `pkg name here`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r echo = F}
knitr::opts_chunk$set(comment=NA, echo = F, message = F, warning = F, out.width = '100%', fig.height = 3)
```

---

&nbsp;

Processing began at: `r format(begin_time, '%Y-%B-%d %H:%M:%S')`.

Processing finished at: `r format(end_time, '%Y-%B-%d %H:%M:%S')`.

`r end_time - begin_time` minutes is how long it took to generate this report.

&nbsp;

## Overall Data Table Report 

&nbsp;

#### First ten rows of data

```{r make_report1, echo=F,warning=F,message=F, comment=NA}
kable(head(df, 10))
```

&nbsp;

#### Column-wise summaries: numerical variables

```{r echo=FALSE}
if (length(dt1) > 0) {
kable(as.data.frame(dt1))
} else if (length(dt1) == 0) {
  print("No numerical variables found.")
}
```

&nbsp;

#### Column-wise: Categorical and character variables

```{r}
if (length(dt3) > 0) {
kable(dt3,n=5e2)
} else if (length(dt3) == 0) {
  print("No categorical/character variables found.")
}
```

&nbsp;

#### Column-wise: Levels in Categorical and character variables

```{r}
if (length(dt2) > 0) {
kable(dt2,n=5e2)
} else if (length(dt2) == 0) {
  print("No categorical/character variables found.")
}
```

&nbsp;

---

## Temporal information


---

## Spatial information

```{r}
xy <- space_detective(data_entity_list)
```


---

&nbsp;

## Variable-by-variable Report

```{r results='asis'}
for (i in 1:length(var_report)){
   cat('\n')
   cat('\n')
   cat(paste("### Variable:", var_report[[i]][["var_name"]]))
   cat('\n')
   print(var_report[[i]][["plots"]][["x"]])
   cat('\n')
   print(var_report[[i]][["missing"]])
   cat('\n')
   print(var_report[[i]][["space"]][[1]])
   cat('\n')
   print(var_report[[i]][["space"]][[2]])
   cat('\n')
}
```