---
title: "`r report_title`"
author: "Generated by `pkg name here`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document
---

```{r echo = F}
knitr::opts_chunk$set(comment=NA, echo = F, out.width = '100%', fig.height = 3)
```

---

&nbsp;

Processing began at: `r format(begin_time, '%Y-%B-%d %H:%M:%S')`.

Processing finished at: `r format(end_time, '%Y-%B-%d %H:%M:%S')`.

`r end_time - begin_time` minutes is how long it took to generate this report.

&nbsp;

## Overall Data Table Report 

&nbsp;

#### First ten rows of data

```{r make_report1, echo=F,warning=F,message=F, comment=NA}
kable(head(df, 10))
```

&nbsp;

#### Column-wise summaries: numerical variables

```{r echo=FALSE}
kable(as.data.frame(dt1))
```

&nbsp;

#### Column-wise summaries: Categorical and character variables

```{r}
kable(dt3,n=5e2)
```

&nbsp;

#### Column-wise summaries: Levels in Categorical and character variables

```{r}
kable(dt2,n=5e2)
```

&nbsp;

---
## Temporal information

```{r}

```

---

## Spatial information

```{r}
xy <- space_detective(data_entity_list)
```


---

&nbsp;

## Variable-by-variable Report

```{r echo=FALSE, message=FALSE, warning=FALSE, comment = NA}
var_report
```